Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
More added to disc

Therefore, we think our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified.

>>>>

Therefore, we think our argument that the \MgFe{} does not decline quickly enough at high-$z$ is reasonably justified. An intuitive understanding of the impact the decline in \alphaFe{} vs time has is that, when \alphaFe{} declines rapidly, it is a better estimator of age. When it is a better estimator of age, events separated temporally better separate in the abundance plane.

\subsection{Comparison to Observations}\label{ssec:compare_obs}
The lower left panel of Figure~\ref{fig:alpha} shows the \MgFe{} vs age of stars in bins of \FeH{} which pass our solar neighborhood selection and are present in the APOKASC2 catalog. In the bins where the bimodality is strongest (blue and orange, $\FeH=-0.5$ and $-0.25$, respectively), we see that there is a sort of two tiered distribution with significant overlap in age. In the SoI with age and abundance errors shown in the lower right panel, a very similar distribution can be seen in all \FeH{} bins. An examination of the true distribution in the SoI (upper right panel), we see that the two distributions are in fact very cleanly separated in age. Of course, we do not know the true underlying distribution in the Milky Way, but these panels show that the Milky Way is consistent with the general picture shown in our SoI.
